Cybersecurity in UK Higher Education?

### 2019-09-16 ITNow_TP_v2.tex

\begin{strapline}
"Every Computer Science Degree Should Require a Course in Cybersecurity". We explore the progress to date.
\end{strapline}

@@

On the 27th August of this year the Harvard Business Review reported "Every Computer Science Degree Should Require a Course in Cybersecurity". How could you argue with the intent of this suggestion? The BCS has been promoting this for a number of years and how fantastic to see our concerns highlighted to such an audience. But, and this is a subtly but significant \textit{'but'}, is this the best approach? We feel not. As our recent research {\cite{Cricketal2019}} has argued cybersecurity is too important to be left to specialists and needs to be everyone's responsibility and addressed across a course.

This article explores some challenges regarding how cybersecurity is taught which informs this view and provides a progress report regarding BCS efforts to promote the inclusion of cybersecurity in degree course.

@@

\section*{Challenges} \label{sec}
% TC: pick a couple of these as examples?
\subsection*{Educational Resources}\label{sec:EDResource}
%It is hard to determine what is actually delivered as part of a degree programme, but a reasonable proxy for this are recommended textbooks and other supporting resources.
Lets start by looking at the books and other resources that are used to teach degrees. Do these support the promotion of good cybersecurity practices? As you will see, a single course on the subject may not be enough. We think that would be like \textit{'shutting the proverbial stable door after the horse has bolted'}. 
\subsubsection*{Databases}\label{sec:SQL}
A core part of any computer science degree. SQL injection is a major weakness: number one in the Open Web Application Security Project (OWASP) Top 10, and has been in the Top 10 since at least 2003. Database textbooks were analysed in 2019 ~\cite{Drop2019}.  This work shows this flaw is not being addressed. Small wonder it continues to be an issue!

\subsubsection*{The Case of Java}\label{sec:Java}
Our research shows Java is still the most commonly taught programme language at universities in the UK. Many Java books do not cover security.  If you want to know about security you need to look at the documentation of the package/API being used, and/or  informal resources. \cite{Mengetal2018a} analysed this and Stack Overflow in particular. Looking at the Spring Framework 53\% of questions related to cybersecurity were dominated by authentication (45\%). One example being, by default, Spring enables protection against cross-site request forgery (CSRF). But all the accepted answers to CSRF-related failures simply suggested disabling the check. There were no negative comments about this, and indeed a typical response is ``{\emph{Adding}} \verb!csrf().disable()!
{\emph{{solved the issue!!! I have no idea why it was enabled by default}}''. } Quite concerning!

\subsubsection*{Informal Resources}\label{sec:informal}
The web abounds with informal resources, such as tutorials and code snippets. How good are these? One investigation \cite{Unruhetal2017a} considered 30 popular tutorials and found six had SQL injection weaknesses, and three had Cross-Site Scripting (Number 7 in OWASP's Top Ten) weaknesses. Looking for related code fragments on GitHub, found 820 instances of these fragments, of which 117 were verified manually to be vulnerable --- 80\% of which were vulnerable to SQL injection. Hardly encouraging.

@@

\subsection*{Who will teach the Cybersecurity?}\label{sec:staffing}
Enough about the books, who is going to teach this? Cybersecurity skills are in short supply, in both industry and academia. The demand for cybersecurity skills in industry makes it difficult for academia to attract academics with knowledge, practical experience, research background and academic aspirations. As universities expand their cybersecurity provision it is not uncommon to find multiple jobs advertised at the same time.

@@

Enough of the challenges. What have we been doing about it? The BCS has been using the accreditation process to mandate formal inclusion of information security (2010) and then cybersecurity (2013) within the programmes we accredit.

@@

In summary, this shows that many accredited institutions have now embedded cybersecurity in their provision, a number are in the process of doing so and a minority have chosen not to.

@@

The BCS is improving the cybersecurity capacity in the UK by enhancing the education experience of the students on BCS accredited degree programmes. If you want to be reassured that the graduates you recruit have some cyber knowledge, then seek a BCS accredited degree. There are challenges ahead in terms of enhancing the resources upon which the degree provision depends.

Is it sufficient to leave to cybersecurity to Computer Scientist? We hope this is conversation that will begin shortly.

>>>>

\begin{strapline}
Including cybersecurity in university education. We explore the progress to date.
\end{strapline}

@@

On the 27th August of this year the Harvard Business Review reported "Every Computer Science Degree Should Require a Course in Cybersecurity". How could you argue with the intent of this suggestion? The BCS has been promoting this for a number of years and how fantastic to see our concerns highlighted to such an audience. As our recent research {\cite{Cricketal2019}} has argued cybersecurity is too important to be left to specialists and hence is an essential inclusion in Computer Science, Information Technology and all other related degree programmes.

This article explores some challenges related to the teaching of cybersecurity and provides a progress report regarding BCS efforts to promote the inclusion of cybersecurity in accredited degree programmes.

@@

\section*{Challenges} \label{sec}
% TC: pick a couple of these as examples?
\subsection*{Educational Resources}\label{sec:EDResource}
%It is hard to determine what is actually delivered as part of a degree programme, but a reasonable proxy for this are recommended textbooks and other supporting resources.
Let's start by looking at the books and other resources that are used to teach degrees. Do these support the promotion of good cybersecurity practices? As you will see, that whilst progress has been made, there still appears to be work to do.
\subsubsection*{Databases}\label{sec:SQL}
A core part of any computer science degree. SQL injection is a major weakness: number one in the Open Web Application Security Project (OWASP) Top 10, and has been in the Top 10 since at least 2003. Database textbooks were analysed in 2019 ~\cite{Drop2019}.  This work shows this flaw is not commonly being addressed in database textbooks. Small wonder it continues to be an issue!

\subsubsection*{The Case of Java}\label{sec:Java}
Our research shows Java is still the most commonly taught programming language at universities in the UK. Many Java books do not cover security.  If you want to know about security you need to look at the documentation of the package/API being used, and/or  informal resources. \cite{Mengetal2018a} analysed this and Stack Overflow in particular. We also know our students love resources like Stack Overflow. Looking at the Spring Framework 53\% of questions related to cybersecurity were dominated by authentication (45\%). One example being, by default, Spring enables protection against cross-site request forgery (CSRF). But all the accepted answers to CSRF-related failures simply suggested disabling the check. There were no negative comments about this, and indeed a typical response is ``{\emph{Adding}} \verb!csrf().disable()!
{\emph{{solved the issue!!! I have no idea why it was enabled by default}}''. } Quite concerning!

\subsubsection*{Informal Resources}\label{sec:informal}
The web abounds with informal resources, such as tutorials and code snippets. We know these are very popular with the students we teach. How good are these? One investigation \cite{Unruhetal2017a} considered 30 popular tutorials and found six had SQL injection weaknesses, and three had Cross-Site Scripting (Number 7 in OWASP's Top Ten) weaknesses. Looking for related code fragments on GitHub, found 820 instances of these fragments, of which 117 were verified manually to be vulnerable --- 80\% of which were vulnerable to SQL injection. Hardly encouraging.

@@

\subsection*{Who will teach the Cybersecurity?}\label{sec:staffing}
Who is going to teach this? Cybersecurity skills are in short supply, in both industry and academia. The demand for cybersecurity skills in industry makes it difficult for academia to attract academics with knowledge, practical experience, research background and academic aspirations. As universities expand their cybersecurity provision it is not uncommon to find multiple jobs advertised at the same time.

@@

Enough of the challenges. What have we been doing about it? The BCS has been using the accreditation process to mandate formal inclusion of information security (2010) and then cybersecurity (2013) in accredited programmes.

@@

%In summary, this shows that many accredited institutions have now embedded cybersecurity in their provision, a number are in the process of doing so and a minority have chosen not to.

@@

The BCS is improving the cybersecurity capacity in the UK by enhancing the education experience of the students on BCS accredited degree programmes. If you want to be reassured that the graduates you recruit have some cybersecurity knowledge, then seek a BCS accredited degree. There are challenges ahead in terms of enhancing the resources upon which the degree provision depends and developing the cybersecurity capacity within universities.

As a final rhetorical point, is it sufficient to leave to cybersecurity to Computer Scientist? Should it be solely the preserve of those who work with Tech? Or should it be everyone's responsibility? We hope this is a conversation that will begin shortly.
